---
title: "R_model"
author: "Ben"
date: "4/20/2021"
output:
  word_document: default
  pdf_document: default
  html_document: default
---

```{r echo = TRUE}
library(readr)
library(ggplot2)
library(Hmisc)
library(dplyr)
library(lme4)
library(scales)
#library(RCurl)
library(effects)
```

```{r echo = TRUE}
data = read.csv("C:/Users/Elvinyuan/Desktop/statistics_intern/Hardy/data.csv", na.strings=c("","NA", "-", "-1"))
```
change variables to factors
```{r echo = TRUE}
data$PLACEMENT_TYPE <- factor(data$PLACEMENT_TYPE)
```

Visualizations
visualize the explanatory variables which our client feels interested in on the effect of our response variable. 
```{r echo = TRUE}
ggplot(data=data, aes(y=percentFRL, x=PLACEMENT_TYPE)) +
  geom_boxplot() +
  ylab("Proportion of Corp. Receiving Free/Reduced Lunch") +
  ggtitle("Inclusion By Free/Reduced Rate of Corporation") +
  scale_x_discrete("Inclusion Level", labels = c("1"="High","0"= "Low"))
```

```{r echo = TRUE}
ggplot(data=data, aes(y=schoolSize, x=PLACEMENT_TYPE))+geom_boxplot() +ylab("School Size") +
  ggtitle("Inclusion By School Size") +
  scale_x_discrete("Inclusion Level", labels = c("1"="High","0"= "Low"))
```

```{r echo = TRUE}
ggplot(data=data, aes(x=Ethnicity, fill = forcats::fct_rev(PLACEMENT_TYPE))) +
  geom_bar(position = "fill") +
  scale_y_continuous(labels = scales::percent) +
  ylab("Percent Inclusion") +
  xlab("Ethnicity") +
  ggtitle("Inclusion Rate by Ethnicity") +
  theme(legend.position = "none") +
  scale_fill_grey(start = 1, end = 0) +
  coord_flip()
```

```{r echo = TRUE}
ggplot(data = data, aes(x=GENDER_CODE, fill = forcats::fct_rev(PLACEMENT_TYPE))) +
  geom_bar(position = "fill") +
  scale_y_continuous(labels = scales::percent) +
  ylab("Percent Inclusion") +
  xlab("Gender") +
  ggtitle("Inclusion Rate by Gender") +
  theme(legend.position = "none") +
  scale_fill_grey(start = 1, end = 0) +
  coord_flip()
```

```{r echo = TRUE}
ggplot(data=data, aes(y=percentWhite, x=PLACEMENT_TYPE)) +
  geom_boxplot() +
  ylab("Proportion of White") +
  ggtitle("Inclusion By Proportion of White") +
  scale_x_discrete("Inclusion Level", labels = c("1"="High","0"= "Low"))
```

```{r echo = TRUE}
ggplot(data=data, aes(y=discLength, x=PLACEMENT_TYPE))+geom_boxplot() +ylab("Behavior") +
  ggtitle("Inclusion By Behavior") +
  scale_x_discrete("Inclusion Level", labels = c("1"="High","0"= "Low"))
```

```{r echo = TRUE}
ggplot(data=data, aes(y=discCount, x=PLACEMENT_TYPE))+geom_boxplot() +ylab("Behavior") +
  ggtitle("Inclusion By Behavior") +
  scale_x_discrete("Inclusion Level", labels = c("1"="High","0"= "Low"))
```

Make our first round of models

```{r echo = TRUE}
model1 <- glmer(PLACEMENT_TYPE ~  percentFRL + (1|SCHOOL_YEAR_ID), data = data, family = binomial,control=glmerControl(optimizer="bobyqa"))
```

```{r echo = TRUE}
print(model1, corr = FALSE)
```

```{r echo = TRUE}
se1 <- sqrt(diag(vcov(model1)))
# table of estimates with 95% CI
(tab1 <- cbind(Est = fixef(model1), LL = fixef(model1) - 1.96 * se1, UL = fixef(model1) + 1.96 *se1))
exp(tab1)
```
So the fixed effect is significant.

```{r echo = TRUE}
#model2 <- glmer(PLACEMENT_TYPE ~  schoolSize + (1|SCHOOL_YEAR_ID), data = data, family = binomial,control=glmerControl(optimizer="bobyqa"))
```
Model failed to converge becasue schoolsize and Placement_type are in the different magnitude. If we insist to do the model, we have to rescale variables, but it might change the meaning of schoolsize.

```{r echo = TRUE}
model3 <- glmer(PLACEMENT_TYPE ~   Ethnicity + (1|SCHOOL_YEAR_ID), data = data, family = binomial,control=glmerControl(optimizer="bobyqa"))
```

```{r echo = TRUE}
print(model3, corr = FALSE)
```

```{r echo = TRUE}
se3 <- sqrt(diag(vcov(model3)))
# table of estimates with 95% CI
(tab3 <- cbind(Est = fixef(model3), LL = fixef(model3) - 1.96 * se3, UL = fixef(model3) + 1.96 *se3))
exp(tab3)
```

```{r echo = TRUE}
model4 <- glmer(PLACEMENT_TYPE ~   GENDER_CODE*Ethnicity + (1|SCHOOL_YEAR_ID), data = data, family = binomial,control=glmerControl(optimizer="bobyqa"))
```

```{r echo = TRUE}
print(model4, corr = FALSE)
```

```{r echo = TRUE}
se4 <- sqrt(diag(vcov(model4)))
# table of estimates with 95% CI
(tab4 <- cbind(Est = fixef(model4), LL = fixef(model4) - 1.96 * se4, UL = fixef(model4) + 1.96 *se4))
exp(tab4)
```

```{r echo = TRUE}
plot(Effect(c("GENDER_CODE"，"Ethnicity"), model4), lines=list(multiline=TRUE),
confint=list(style="bars"))
```


```{r echo = TRUE}
model5 <- glmer(PLACEMENT_TYPE ~   percentWhite*Ethnicity + (1|SCHOOL_YEAR_ID), data = data, family = binomial,control=glmerControl(optimizer="bobyqa"))
```


```{r echo = TRUE}
plot(Effect(c("percentWhite"，"Ethnicity"), model5), lines=list(multiline=TRUE),
confint=list(style="bars"))
```



```{r echo = TRUE}
print(model5, corr = FALSE)
```


```{r echo = TRUE}
se5 <- sqrt(diag(vcov(model5)))
# table of estimates with 95% CI
(tab5 <- cbind(Est = fixef(model5), LL = fixef(model5) - 1.96 * se5, UL = fixef(model5) + 1.96 *se5))
exp(tab5)
```

```{r echo = TRUE}
model6 <- glmer(PLACEMENT_TYPE ~   discLength*GENDER_CODE + (1|SCHOOL_YEAR_ID), data = data, family = binomial,control=glmerControl(optimizer="bobyqa"))
```

```{r echo = TRUE}
plot(Effect(c("discLength"，"GENDER_CODE"), model6), lines=list(multiline=TRUE),
confint=list(style="bars"))
```

```{r echo = TRUE}
print(model6, corr = FALSE)
```

```{r echo = TRUE}
se6 <- sqrt(diag(vcov(model6)))
# table of estimates with 95% CI
(tab6 <- cbind(Est = fixef(model6), LL = fixef(model6) - 1.96 * se6, UL = fixef(model6) + 1.96 *se6))
exp(tab6)
```

```{r echo = TRUE}
model6.2 <- glmer(PLACEMENT_TYPE ~   discCount*GENDER_CODE + (1|SCHOOL_YEAR_ID), data = data, family = binomial,control=glmerControl(optimizer="bobyqa"))
```

```{r echo = TRUE}
plot(Effect(c("discCount"，"GENDER_CODE"), model6.2), lines=list(multiline=TRUE),
confint=list(style="bars"))
```

```{r echo = TRUE}
print(model6.2, corr = FALSE)
```

```{r echo = TRUE}
se6.2 <- sqrt(diag(vcov(model6.2)))
# table of estimates with 95% CI
(tab6.2 <- cbind(Est = fixef(model6.2), LL = fixef(model6.2) - 1.96 * se6.2, UL = fixef(model6.2) + 1.96 *se6.2))
exp(tab6.2)
```

```{r echo = TRUE}
model7 <- glmer(PLACEMENT_TYPE ~   GRADE_CODE + (1|SCHOOL_YEAR_ID), data = data, family = binomial,control=glmerControl(optimizer="bobyqa"))
print(model7, corr = FALSE)
se7 <- sqrt(diag(vcov(model7)))
# table of estimates with 95% CI
(tab7 <- cbind(Est = fixef(model7), LL = fixef(model7) - 1.96 * se7, UL = fixef(model7) + 1.96 *se7))
exp(tab7)
```
Our model did fit, but it generated that warning because our random effects are very small.

```{r echo = TRUE}
model8 <- glmer(PLACEMENT_TYPE ~   ENGLISH_LEARNER_STATUS_CODE + (1|SCHOOL_YEAR_ID), data = data, family = binomial,control=glmerControl(optimizer="bobyqa"))
print(model8, corr = FALSE)
se8 <- sqrt(diag(vcov(model8)))
# table of estimates with 95% CI
(tab8 <- cbind(Est = fixef(model8), LL = fixef(model8) - 1.96 * se8, UL = fixef(model8) + 1.96 *se8))
exp(tab8)
```

```{r echo = TRUE}
model9 <- glmer(PLACEMENT_TYPE ~   SOCIO_ECON_STATUS_CODE + (1|SCHOOL_YEAR_ID), data = data, family = binomial,control=glmerControl(optimizer="bobyqa"))
print(model9, corr = FALSE)
se9 <- sqrt(diag(vcov(model9)))
# table of estimates with 95% CI
(tab9 <- cbind(Est = fixef(model9), LL = fixef(model9) - 1.96 * se9, UL = fixef(model9) + 1.96 *se9))
exp(tab9)
```

```{r echo = TRUE}
model10 <- glmer(PLACEMENT_TYPE ~   percentSPED + (1|SCHOOL_YEAR_ID), data = data, family = binomial,control=glmerControl(optimizer="bobyqa"))
print(model10, corr = FALSE)
se10 <- sqrt(diag(vcov(model10)))
# table of estimates with 95% CI
(tab10 <- cbind(Est = fixef(model10), LL = fixef(model10) - 1.96 * se10, UL = fixef(model10) + 1.96 *se10))
exp(tab10)
```

```{r echo = TRUE}
model11 <- glmer(PLACEMENT_TYPE ~   absent + (1|SCHOOL_YEAR_ID), data = data, family = binomial,control=glmerControl(optimizer="bobyqa"))
print(model11, corr = FALSE)
se11 <- sqrt(diag(vcov(model11)))
# table of estimates with 95% CI
(tab11 <- cbind(Est = fixef(model11), LL = fixef(model11) - 1.96 * se11, UL = fixef(model11) + 1.96 *se11))
exp(tab11)
```

The model that we think our client will feel interested 
```{r echo = TRUE}
model2_1 <- glmer(PLACEMENT_TYPE ~ GENDER_CODE + ENGLISH_LEARNER_STATUS_CODE + SOCIO_ECON_STATUS_CODE + Ethnicity  + percentWhite + percentSPED + percentFRL + discCount + absent + GENDER_CODE:Ethnicity + Ethnicity:percentWhite + discCount:GENDER_CODE + (1|SCHOOL_YEAR_ID), data = data, family = binomial,control=glmerControl(optimizer="bobyqa"))
```

```{r echo = TRUE}
print(model2_1, corr = FALSE)
se2_1 <- sqrt(diag(vcov(model2_1)))
# table of estimates with 95% CI
(tab2_1 <- cbind(Est = fixef(model2_1), LL = fixef(model2_1) - 1.96 * se2_1, UL = fixef(model2_1) + 1.96 *se2_1))
exp(tab2_1)
```

```{r echo = TRUE}
plot(Effect(c("discCount"，"GENDER_CODE"), model2_1), lines=list(multiline=TRUE),
confint=list(style="bars"))
```

```{r echo = TRUE}
plot(Effect(c("Ethnicity","percentWhite"), model2_1), lines=list(multiline=TRUE),
confint=list(style="bars"))
```

```{r echo = TRUE}
plot(Effect(c("GENDER_CODE","Ethnicity"), model2_1), lines=list(multiline=TRUE),
confint=list(style="bars"))
```

model checking
```{r echo = TRUE}
qqnorm(residuals(model2_1))
```
It is OK


