---
title: "R_model"
author: "Ben"
date: "4/20/2021"
output:
  word_document: default
  pdf_document: default
  html_document: default
---

```{r echo = TRUE}
library(readr)
library(ggplot2)
library(Hmisc)
library(dplyr)
library(lme4)
library(scales)
#library(RCurl)
library(effects)
library(MASS)
library(sjPlot)
library(car)
library(GGally)
```

```{r echo = TRUE}
data = read.csv("ad.data.csv", na.strings=c("","NA", "-", "-1"))
data$PLACEMENT_TYPE <- factor(data$PLACEMENT_TYPE)
data$ENGLISH_LEARNER_STATUS_CODE = factor(data$ENGLISH_LEARNER_STATUS_CODE)
data$SOCIO_ECON_STATUS_CODE = factor(data$SOCIO_ECON_STATUS_CODE)
data$GRADE_CODE = factor(data$GRADE_CODE)
data$schoolSize = data$schoolSize / 1000

# rescale to make closer
data[is.na(data$absent), 19] = 0
data$absent = data$absent/180
```


```{r}
model = glmer(PLACEMENT_TYPE ~ GRADE_CODE + GENDER_CODE + ENGLISH_LEARNER_STATUS_CODE + SOCIO_ECON_STATUS_CODE + Ethnicity  + percentWhite + percentSPED + percentFRL + corpWhite + corpSPED + corpFRL + absent + (1|STUDENT_ALTERNATE_ID), data = data, family = binomial, control=glmerControl(optimizer="bobyqa"))

plot_model(m1, show.values = T)

```

If we put all the variables into one model (except spending per student, school size, and discipline) we can see the significance of each variable.  

```{r}
ggpairs(data[, c(8, 10:16)])
```

Looking at variables separately:

```{r echo = TRUE}
ggplot(data = data, aes(x=GRADE_CODE, fill = PLACEMENT_TYPE)) +
  geom_bar(position = "fill") +
  scale_y_continuous(labels = scales::percent) +
  ylab("Percent Inclusion") +
  xlab("Grade") +
  ggtitle("Inclusion Rate by Grade") +
  theme(legend.position = "none") +
  scale_fill_grey(start = 1, end = 0) +
  coord_flip()
```

```{r echo = TRUE}
ggplot(data = data, aes(x=GENDER_CODE, fill = PLACEMENT_TYPE)) +
  geom_bar(position = "fill") +
  scale_y_continuous(labels = scales::percent) +
  ylab("Percent Inclusion") +
  xlab("Gender") +
  ggtitle("Inclusion Rate by Gender") +
  theme(legend.position = "none") +
  scale_fill_grey(start = 1, end = 0) +
  coord_flip()
```

```{r echo = TRUE}
ggplot(data = data, aes(x=ENGLISH_LEARNER_STATUS_CODE, fill = PLACEMENT_TYPE)) +
  geom_bar(position = "fill") +
  scale_y_continuous(labels = scales::percent) +
  ylab("Percent Inclusion") +
  xlab("ELL Status") +
  ggtitle("Inclusion Rate by English Learner Status") +
  theme(legend.position = "none") +
  scale_fill_grey(start = 1, end = 0) +
  coord_flip()
```

```{r echo = TRUE}
ggplot(data = data, aes(x=SOCIO_ECON_STATUS_CODE, fill = PLACEMENT_TYPE)) +
  geom_bar(position = "fill") +
  scale_y_continuous(labels = scales::percent) +
  ylab("Percent Inclusion") +
  xlab("FRL status") +
  ggtitle("Inclusion Rate by Free/Reduced Lunch Status") +
  theme(legend.position = "none") +
  scale_fill_grey(start = 1, end = 0) +
  coord_flip()
```

```{r echo = TRUE}
ggplot(data=data, aes(x=Ethnicity, fill = PLACEMENT_TYPE)) +
  geom_bar(position = "fill") +
  scale_y_continuous(labels = scales::percent) +
  ylab("Percent Inclusion") +
  xlab("Ethnicity") +
  ggtitle("Inclusion Rate by Ethnicity") +
  theme(legend.position = "none") +
  scale_fill_grey(start = 1, end = 0) +
  coord_flip()
```

```{r include = F}
model10 <- glmer(PLACEMENT_TYPE ~  absent + (1|STUDENT_ALTERNATE_ID), data = data, family = binomial,control=glmerControl(optimizer="bobyqa"))
plot_model(model10, show.values = T)
summary(model10)
exp(-5.43/180)
```
Each day of absence correlates with a 3% drop in odds of inclusion

```{r include = F}
model11 <- glmer(PLACEMENT_TYPE ~  discipline + (1|STUDENT_ALTERNATE_ID), data = data, family = binomial,control=glmerControl(optimizer="bobyqa"))
plot_model(model11, show.values = T)
```
Discipline has no significant effect

```{r include = F}
model1 <- glmer(PLACEMENT_TYPE ~  percentFRL + (1|STUDENT_ALTERNATE_ID), data = data, family = binomial,control=glmerControl(optimizer="bobyqa"))
plot_model(model1, show.values = T)
summary(model1)
1-exp(-.177)
```
A 10% increase in percent of the school on Free and Reduced Lunches correlates with a 16% drop in the odds of being included.

```{r include = F}
model2 <- glmer(PLACEMENT_TYPE ~  percentWhite + (1|STUDENT_ALTERNATE_ID), data = data, family = binomial,control=glmerControl(optimizer="bobyqa"))
plot_model(model2, show.values = T)
summary(model2)
exp(.8468)
```

A 10% increase in the percent of student body which is white correlates with an 9% increase in odds of inclusion.

```{r include = F}
model3 <- glmer(PLACEMENT_TYPE ~  percentSPED + (1|STUDENT_ALTERNATE_ID), data = data, family = binomial,control=glmerControl(optimizer="bobyqa"))
plot_model(model3, show.values = T)
summary(model3)
exp(-1.51)
```
A 10% increase in the percent of student body which is in special education correlates with a 87% drop in odds of inclusion.

```{r include = F}
model4 <- glmer(PLACEMENT_TYPE ~  schoolSize + (1|STUDENT_ALTERNATE_ID), data = data, family = binomial,control=glmerControl(optimizer="bobyqa"))
plot_model(model4, show.values = T)
```

School size is not significant.

```{r include = F}
model5 <- glmer(PLACEMENT_TYPE ~  corpWhite + (1|STUDENT_ALTERNATE_ID), data = data, family = binomial,control=glmerControl(optimizer="bobyqa"))
plot_model(model5, show.values = T)
summary(model5)
exp(.178)
```
Each 10% increase in percent of the corporation that is white correlates with a 19% increase in odds of incusion.

```{r include = F}
model6 <- glmer(PLACEMENT_TYPE ~  corpFRL + (1|STUDENT_ALTERNATE_ID), data = data, family = binomial,control=glmerControl(optimizer="bobyqa"))
plot_model(model6, show.values = T)
summary(model6)
exp(-.216)
```
Each 10% increase in percent of students on FRL in the corporation correlates with a 19% drop in odds of inclusion

```{r include = F}
model7 <- glmer(PLACEMENT_TYPE ~  corpSPED + (1|STUDENT_ALTERNATE_ID), data = data, family = binomial,control=glmerControl(optimizer="bobyqa"))
plot_model(model7, show.values = T)
summary(model7)
exp(-.181)
```
Each 1% increase in the percent of the corporation in special education corresponds with a 17% drop in odds of inclusion.

```{r include = F}
m1 <- glmer(PLACEMENT_TYPE ~  Ethnicity*GENDER_CODE + (1|STUDENT_ALTERNATE_ID), data = data, family = binomial, control=glmerControl(optimizer="bobyqa"))

plot_model(m1, show.values = T)
# all have a significant effect
plot(Effect(c("GENDER_CODE", "Ethnicity"), m1), lines=list(multiline=TRUE))
```

```{r include = F}
m2 <- glmer(PLACEMENT_TYPE ~  Ethnicity*percentWhite + (1|STUDENT_ALTERNATE_ID), data = data, family = binomial, control=glmerControl(optimizer="bobyqa"))

plot_model(m2, show.values = T)
# all have a significant effect
plot(Effect(c("percentWhite", "Ethnicity"), m2), lines=list(multiline=TRUE))
```

```{r include = F}
m3 <- glmer(PLACEMENT_TYPE ~  GENDER_CODE*discipline + (1|STUDENT_ALTERNATE_ID), data = data, family = binomial, control=glmerControl(optimizer="bobyqa"))

plot_model(m3, show.values = T)
# none have a significant effect
#plot(Effect(c("GENDER_CODE", "discipline"), m3), lines=list(multiline=TRUE), confint=list(style="bars"))
```

```{r include = F}
m4 <- glmer(PLACEMENT_TYPE ~  Ethnicity*percentFRL + (1|STUDENT_ALTERNATE_ID), data = data, family = binomial, control=glmerControl(optimizer="bobyqa"))

plot_model(m4, show.values = T)
# all have a significant effect
plot(Effect(c("percentFRL", "Ethnicity"), m4), lines=list(multiline=TRUE))
```

```{r include = F}
m5 <- glmer(PLACEMENT_TYPE ~  Ethnicity*percentWhite + (1|STUDENT_ALTERNATE_ID), data = data, family = binomial, control=glmerControl(optimizer="bobyqa"))

plot_model(m5, show.values = T)
# all have a significant effect
plot(Effect(c("percentWhite", "Ethnicity"), m5), lines=list(multiline=TRUE))
```

```{r include = F}
m6 <- glmer(PLACEMENT_TYPE ~  schoolSize*percentWhite + (1|STUDENT_ALTERNATE_ID), data = data, family = binomial, control=glmerControl(optimizer="bobyqa"))

plot_model(m6, show.values = T)
# all have a significant effect
plot(Effect(c("percentWhite", "schoolSize"), m6), lines=list(multiline=TRUE))
```